Community-conditioned language models for linguistic variation

### 2021-10-14 paper/paper1.tex
flyspell
wibble

@@

Thus if the real \(d(L,S)\) is below the mean by several standard
deviations, we can safely assume that there is statistically
significant correlation between \(L\) and \(S\). A 4-sigma difference
has less than one percent chance of occurring randomly. In our case:
we observe a difference between 61 and 68 standard deviations
(\cref{tab:embedding-correlations}). This definitely indicates a
significant correlation.  Furthermore, by coming back to the
definition of \(d(L,S)\), we know that, on average, the cosine
similarity between \(ΩL\) and \(S\) is \(510 - 232.18 / 510\).  It
further means that if we obtain a linguistic embedding \(L_k\) for a
new community $k$, we can estimate its social embedding by \(ΩL_k\),
and the cosine similarity with its true social embedding \(S_k\) is
expected to be \((431.39 - 232.18) / 510\) --- accounting for
over-fitting effects by taking the average distance rather than the
maximum. % JP: TODO is the number from the table. this should probably be rewritten
In sum, it is clear that the CCLM embeddings predict some aspect the social-network embeddings--- but far from all of it.

>>>>

% -*- eval: (flyspell-mode 1); -*-

@@

Thus if the real \(d(L,S)\) is below the mean by several standard
deviations, we can safely assume that there is statistically
significant correlation between \(L\) and \(S\). A 4-sigma difference
has less than one percent chance of occurring randomly. In our case:
we observe a difference between 61 and 68 standard deviations
(\cref{tab:embedding-correlations}). This definitely indicates a
significant correlation.  Furthermore, by coming back to the
definition of \(d(L,S)\), we know that, on average, the cosine
similarity between \(ΩL\) and \(S\) is \(0.45 = \) (\(510 - 232.18 / 510\)).  It
further means that if we obtain a linguistic embedding \(L_k\) for a
new community $k$, we can estimate its social embedding by \(ΩL_k\),
and the cosine similarity with its true social embedding \(S_k\) is
expected to be \(0.39\) = \((431.39 - 232.18) / 510\) --- accounting for
over-fitting effects by taking the average distance rather than the
maximum. % JP: TODO is the number from the table. this should probably be rewritten
In sum, it is clear that the CCLM embeddings predict some aspect the social-network embeddings--- but far from all of it.
